Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-10 main.tex
Fixes

The {\em underlying} step function, $\mathord{\stepstounderfull} \in \MACHS
\rightharpoonup \MACHS$, embodies the standard RISC-V ISA semantics.

@@

The {\em observation trace} arising from an infinite sequence of contours
and machine states $(\contour_0,\mach_0),\, (\contour_1,\mach_1),\ldots$,
written $\obstrace((\contour_0,\mach_0),\, (\contour_1,\mach_1),\ldots)$
 is
the (finite or infinite) sequence of {\em distinct} values taken on by the
{\em observable} components of each state.  \iftext\bcp{Give an example and
  write it out formally.}\fi \bcp{Question: This could be defined in two
  ways, and I'm not sure which is better or if it really matters: the
  observation trace is a sequence of partial maps from components to their
  values, or the observation trace is a partial maps from components to
  their sequences of observable values.  This starts getting a bit
  technically tangled, but I don't see a simpler alternative right now.}

>>>>

The {\em underlying} step function, $\mathord{\stepstounderfull} \in \MACHS
\rightarrow \MACHS$, embodies the standard RISC-V ISA semantics.

@@

The {\em observation trace} arising from an infinite sequence of contours
and machine states $(\contour_0,\mach_0),\, (\contour_1,\mach_1),\ldots$,
written $\obstrace((\contour_0,\mach_0),\, (\contour_1,\mach_1),\ldots)$
 is
the (finite or infinite) sequence of {\em distinct} values taken on by the
{\em observable} components of each state.  \iftext\bcp{Give an example and
  write it out formally.}\fi \bcp{Question: This could be defined in two
  ways, and I'm not sure which is better or if it really matters: the
  observation trace is a sequence of partial maps from components to their
  values, or the observation trace is a partial maps from components to
  their sequences of observable values.  This starts getting a bit
  technically tangled, but I don't see a simpler alternative right now.
  Answer: map from components to sequences of words.}
